### 2016-08-23 syntax.tex
syntax

A Bloom filter with secret hash functions is captured by setting
$\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
Related constructions that use a secret key~$K$, but not for hashing (e.g. the PRP-based
construction from NY), are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.

The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, falls within our syntax by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.  Similarly the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$. \tsnote{Check the correctness of this claim.}

>>>>

A Bloom filter with secret hash functions is captured by setting
$\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
Related constructions that use a secret key~$K$, but not for hashing (e.g.\ the PRP-based
construction from NY), are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.

By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture he
so-called ``garbled Bloom filter'' due to Dong, Chen and
Wen~\cite{xxx}.  This stores xor-shares of bitstring~$x \in S$ at
positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array.  Similarly, the
cuckoo-hashing construction from NY, which (loosely speaking) stores a
hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$,
is captured when $L=|g(x)|$. \tsnote{Check the correctness of this claim.}
